---
title: "Lohit's test data"
author: "Nicole Williamson"
date:  "`r Sys.Date()`"
output:  
  html_document:
    toc: yes
    toc_depth: 5
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '5'
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Helpful Tips  

**Useful keyboard shortcuts**
*these work for windows, they may be different for Macs*

- `Cntrl` + `Z` functions like the Undo button in word or excel. Undoes whatever action you just did
- `Cntrl` + `Alt` + `I` inserts a new code chunk
- `Cntrl` + `Enter` runs the code that your courser is on (good for if you want to run small sections of code within a larger code chunk)
- `Cntrl` + `F` allows you to find things within the document (can be useful if you want to replace the name of an object everywhere in the document at the same time)
- `Cntrl` + `Shift` + `O` opens a document outline that you can use to quickly navigate between titled sections of your document 
- `Cntrl` + `C` to copy, `Cntrl` + `V` to paste
- `Cntrl` + `S` to save

Use `rm(list = ls())` to Clear workspace (if desired/needed). If run correctly will clear everything from your environment tab. Typically it's good to do this at the start of each of your sessions. Defiantly should do it if you open a new Rmd file.
```{r, echo = FALSE}
rm(list = ls())
```

Use this`getwd()` to check working directory. Will most likely be whatever folder your Rmd file is in. If you need to change it for some reason use `setwd()` 
```{r, echo = FALSE, include=FALSE}
getwd()
#setwd()
```

# Downloading/loading packages

Use `install.packages` to download and install a new R package. You only need to do this once, then you can just use `library()` to load it and be able to call functions within it. and load the package libraries.  

**TIP: It's generally considered best practice to keep the commands to call all the packages you need to use at the top of the document**  

`tidyr`, `dplyr`, and `readr` are probably the most commonly used packages for data wrangling/cleaning.`ggplot2` is very common for creating publication quality figures.  

**Note: The order which you install packages is important. Functions with the same names will be masked by packages loaded in after the previous.**  
Ex: The `select()` function from `MASS` will be masked by `select()` from `dplyar` 
```{r, message=FALSE, warning=FALSE}
library("tidyr")
library("dplyr")
library("readr")
library("ggplot2")
```

# Read in data 
```{r}
mydata <- read.csv("../Data/LOHITS_TEST_data.csv")

unique(mydata$Observation.Location)
```
Split the lat/long into two columns 
```{r}
splitdata <- mydata %>% separate(Observation.Location, sep = "\\,", c('lat', 'long')) %>% 
  separate(lat, sep = "\\ ", c('x', 'lat')) %>%
  separate(long, sep = "\\}", c('long', 'y')) %>%
  separate(long, sep = "\\-", c('z', 'long')) %>%
  mutate(lat = as.numeric(lat)) %>% mutate(long = as.numeric(long)) %>%
  mutate(long = long * (-1)) %>%
  select(-x, -y, -z)
```
























